Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-23 WSSSPE3/report/WSSSPE3_review.tex
Section 3: keynote: tiny changes.

The volunteer model meant unpaid labor. On this note, Turk recommended Ashe
Dryden's blog
post\footnote{http://www.ashedryden.com/blog/the-ethics-of-unpaid-labor-and-the-oss-community}
on the ethics of unpaid labor and the open source software community, which
mentions GitHub as one's resume, for example. Often times, a person funded to
work on some scientific project full time has a small amount of time for working
on a piece of software necessary for the project. However, researchers's ability
to participate in that volunteer community is not always the same and it is not
always aligned with their research projects. From Turk's experience, we cannot
always rely on unpaid labor and volunteer time to sustain a piece of
software---that came down to the notions of the top-down and the bottom-up
approaches, the funded versus the grassroot.

>>>>

The volunteer model meant unpaid labor. On this note, Turk recommended Ashe
Dryden's blog
post\footnote{http://www.ashedryden.com/blog/the-ethics-of-unpaid-labor-and-the-oss-community}
on the ethics of unpaid labor and the open source software community, which
mentions GitHub as one's resume, for example. Often times, a person funded to
work on some scientific project full time has a small amount of time for working
on a piece of software necessary for the project. However, a researcher's ability
to participate in that volunteer community is not always the same and it is not
always aligned with the research projects. From Turk's experience, we cannot
always rely on unpaid labor and volunteer time to sustain a piece of
software---that came down to the notions of the top-down and the bottom-up
approaches, the funded versus the grassroot.
